Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-16 paper.qmd
Finalize the video table

- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible (changed in Rendering the model: Done)
- Check spelling is consistently American (Done)
- Check references (Done)
- Add videos - make a list of the videos in the supplementary section, with the number of the figure that it corresponds too. This avoids having captions that are too long and awkward with raw URLs. And it keeps all of this supplementary material in one place.
- Move the notation table to appendix (Done)
- Code clean up: recommend that all of the calculations done with quollr are done with a separate script(s) and put in a scripts directory. Save the resulting data need to make plots and tables. Only code for the plots and tables is directly in the qmd in the final version.

@@

trimesh_removed_mnist <- ggplot() + 
  geom_point(data = tsne_minst_scaled,
             aes(
               x = emb1,
               y = emb2,
               colour = cluster
             ),
             alpha=0.2)+
    geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", c(0.08, 0.93), cex = 2) +
  theme(legend.position = "none")

@@

mnist_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(0.5, 0.5), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-1.1, 0.9), 
  axis_text_size = 4, 
  is_category = TRUE) +
  interior_annotation(label = "b", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
    legend.position = "none"
  )

@@

mnist_proj_tsne_model2 <- plot_proj(
    proj_obj = proj_obj2,
    point_param = c(0.5, 0.3), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    axis_text_size = 3.5, 
    is_category = TRUE) +
  interior_annotation(label = "c", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

>>>>

- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible (changed in Rendering the model: Done)
- Check spelling is consistently American (Done)
- Check references (Done)
- Add videos - make a list of the videos in the supplementary section, with the number of the figure that it corresponds too. This avoids having captions that are too long and awkward with raw URLs. And it keeps all of this supplementary material in one place. (Done)
- Move the notation table to appendix (Done)
- Code clean up: recommend that all of the calculations done with quollr are done with a separate script(s) and put in a scripts directory. Save the resulting data need to make plots and tables. Only code for the plots and tables is directly in the qmd in the final version.

@@

@@

@@
